\TheTitle

### 2017-07-19 paper/background.tex
editing descriptions of algorithm

Git is a distributed version control system that is used in many
open-source and closed-source projects. It enables many developers to
write code simultaneously, working on separate branches of the same
project. Git uses a directed acyclic graph model (DAG) for storing the
necessary information regarding the state of the code at any point in
time. Git refers to nodes of the DAG as commits, not distinguishing
between the code-carrying commits and the structural commits that bring
two branches together. In this paper, we will refer to the individual
commits code-carrying as commits, the structural merge commits as
merges, and refer to both types without discrimination as repository
events.

>>>>

Git is a distributed version control system that is used in many
open-source and closed-source projects. It enables many developers to
write code simultaneously, working on separate branches of the same
project. Git uses a directed acyclic graph model (DAG) for storing the
necessary information regarding the state of the code at any point in
time. Git refers to nodes of the DAG as commits, not distinguishing
between the code-carrying commits and the structural commits that bring
two branches together. In this paper, we will refer to the individual
code-carrying commits as commits, the structural merge commits as
merges, and refer to both types without discrimination as repository
events.

### 2017-07-19 paper/discussion.tex
editing descriptions of algorithm

Seeing that the visualizations of the \mt model are able to assist users
with understanding how commits are integrated, we continue by looking at
ways of improving the algorithm for faster operations, and making the
conversion from DAG to \mt feasible over the internet.

>>>>

The visualizations of the \mt model assist users with understanding how
commits are integrated. We continue by discussing possible methods for
improving the algorithm to directly produce the combined DAG \mt without
a post-processing step and pruning the DAG to improve the performance
and make it feasible to compute over the internet. Furthermore, we look
to generalize the algorithm to work with arbitrary repositories.

### 2017-07-19 paper/model.tex
editing descriptions of algorithm

        \foreach \x in {0, 1, 2, 3, 4, 5, 6, 7, 8}
    \node[shift={(\x, -0.6)}, color=black] {$t_\x$};
  \end{tikzpicture}
  \caption{Example of a sequence of events performed in different
    repositories. The horizontal axis represents time. The branches and
    repositories are aligned horizontally, and color-coded. Each commit
    points to its parent. The initial commit is at time $t_0$, and the
    head is at $t_8$.}
  \label{fig:repoEvents}
%\vspace{-3mm}
\end{figure}

@@

To demonstrate the behaviour of the algorithm, we use a short example,
computing the merge at commit 5 in Figure~\ref{fig:repoEvents}.
$MergeAtMaster$, recurses along the children of the nodes it visits.
Eventually every child of every node along the path will be visited at
least once. Without loss of generality, suppose that the path recursed
along is from node 5 to 6, 9, 10, and finally 12. The depth for each,
except 12 (a merge into the master branch), is initialized to infinity,
the merge into master is blank, and the next merge is blank. Merges into
master trivially have a distance of 0 from the master branch, and it
merges itself into the master branch. The recursion at 12 returns the
triple $(0, \varnothing, 12)$ to the call from 10. 12 is a merge commit
and 10 is not the first parent, so the temporary depth, $d_c$, is
incremented to 1 and the temporary next merge, $next_c$, is changed to
12. 1 is less than infinity, so the depth is set to 1, the merge to 12,
and the next to 12. This returns the triple $(1, 12, 12)$ to the call
from 9. 9 is the first parent of 10, so no changes are made to the
temporary variables. The call to 9 recurses to the second child, 11. 11
is a merge into the master so it returns $(0, \varnothing, 11)$ to the
call from 9. 9 is not the first parent of 11, so the $d_c$ is
incremented to 1 and $next_c$ is changed to 11. The distances $d_c$ and
$d$ are the same, so to break the tie, we use the time. 12 was merged
after 11, so 11 replaces 12 as the merge into the master branch for 9,
as well as being the next merge. The call for 9 returns the triple $(1,
11, 11)$ to the call for 6. 6 is not the first parent of 9, so $d_c$ is
incremented and $next_c$ is changed to 9, as 9 merges 6. 2 is less than
infinity, so the $d$ is changed to 2, the merge to 11, and the next
merge to 9. The call to 6 returns the triple $(2, 11, 9)$ to the call
for 5. The call for 5 recurses on the second child of 5, calling on 7,
which calls 8, and then 9. 9 can continue, but if the implementation of
the algorithm uses memoization, the call to 9 can immediately return the
triple $(1, 11, 11)$ to the call for 8, and avoid an exponential
runtime. 8 is not the first parent of 8, so $d_c$ is incremented to 2
and $next_c$ is changed to 9. 2 is less than infinity, so $d$ is changed
to 2, $merge$ to 11, and $next$ to 9. The call to 8 returns the triple
$(2, 11, 9)$ to the call for 7, which recurses on the second child of 7,
9. 9 returns the triple $(1, 11, 11)$. 7 is the first parent of 9, so
the depth is not incremented. $d_c$ is less than $d$, so $d$ is changed
to 1, $m$ to 11, and $next$ to 11, returning $(1, 11, 11)$ to the call
for 5. $d_c$ is less than $d$, so $d$ is changed to 1, $m$ to 11, and
$next$ to 11. There are no other children, so the function halts.

@@

\begin{figure}[htbp]
        \centering
        \vspace{3mm}
        {\fontsize{7}{9}
        \begin{verbatim}
Merge: 8cbd84f fd8aa2c
Author: Linus Torvalds <torvalds@linux-foundation.org>
Date:   Tue Aug 10 15:38:19 2010 -0700

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache...
...
        \end{verbatim}}\vspace{-5mm}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one-line summaries messages for the 24
                non-merge commits it merged. The ending ``\ldots'' is part of the log
                and represents that other commits were merged.}
        \label{fig:sampleMerge}
  \vspace{2mm}
\end{figure}

We used this information to evaluate the accuracy of the \mt model
extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016 form the Linux
repository. We computed the \mt of every commit until that date. Since
Linus Torvalds mostly does merging directly into the master branch, we
assumed that every merge by Linus is the root of a \mt, later detecting
merges that do not merge into the master branch and removing them from
the set of root merges. As described above, the log of a merge-commit
usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds
using the command \verb|git log --merges --author='Torvalds'| and
compared the number of commits stated in the log message with the number
of commits in the \mt. We also used the summaries
of the commits found in the merge (not necessarily all---see above) to
make sure those commits were in their corresponding \mt For example, for
the merge in Figure~\ref{fig:sampleMerge} we would expect that the \mt
rooted at \mycode{8cbd84f} contains 24 commits, and the one-line
summaries corresponds to commits in that \mt. We also inspected those
with differences to make sure they were true errors. The results can be
summarized as follows:

>>>>

        \foreach \x in {0, 1, 2, 3, 4, 5, 6, 7, 8}
    \node[shift={(\x, -0.6)}, color=black] {$t_\x$};
  \end{tikzpicture}
  \caption{An example sequence of events performed in different
    repositories. The horizontal axis represents time. The branches and
    repositories are aligned horizontally, and color-coded. Each commit
    points to its parent. The initial commit is at time $t_0$, and the
    head is at $t_8$.}
  \label{fig:repoEvents}
%\vspace{-3mm}
\end{figure}

@@

To demonstrate the behaviour of the algorithm, we use a short example,
computing the merge at commit 5 in Figure~\ref{fig:repoEvents}.
$MergeAtMaster$, recurses along the children of the nodes it visits.
Eventually every child of every node along the path will be visited at
least once. Without loss of generality, suppose that the path recursed
along is from node 5 to 6, 9, 10, and finally 12.

The depth for each, except 12 (a merge into the master branch), is
initialized to infinity, the merge into master is blank, and the next
merge is blank. Merges into master trivially have a distance of 0 from
the master branch, and it merges itself into the master branch. The
recursion at 12 returns the triple $(0, \varnothing, 12)$ to the call
from 10. 12 is a merge commit and 10 is not the first parent, so the
temporary depth, $d_c$, is incremented to 1 and the temporary next
merge, $next_c$, is changed to 12. 1 is less than infinity, so the depth
is set to 1, the merge to 12, and the next to 12. This returns the
triple $(1, 12, 12)$ to the call from 9. 9 is the first parent of 10, so
no changes are made to the temporary variables.

The call to 9 recurses to the second child, 11. 11 is a merge into the
master so it returns $(0, \varnothing, 11)$ to the call from 9. 9 is not
the first parent of 11, so the $d_c$ is incremented to 1 and $next_c$ is
changed to 11. The distances $d_c$ and $d$ are the same, so to break the
tie, we use the time. 12 was merged after 11, so 11 replaces 12 as the
merge into the master branch for 9, as well as being the next merge. The
call for 9 returns the triple $(1, 11, 11)$ to the call for 6. 6 is not
the first parent of 9, so $d_c$ is incremented and $next_c$ is changed
to 9, as 9 merges 6. 2 is less than infinity, so the $d$ is changed to
2, the merge to 11, and the next merge to 9. The call to 6 returns the
triple $(2, 11, 9)$ to the call for 5.

The call for 5 recurses on the second child of 5, calling on 7, which
calls 8, and then 9. 9 can continue, but if the implementation of the
algorithm uses memoization, the call to 9 can immediately return the
triple $(1, 11, 11)$ to the call for 8, and avoid an exponential
runtime. 8 is not the first parent of 8, so $d_c$ is incremented to 2
and $next_c$ is changed to 9. 2 is less than infinity, so $d$ is changed
to 2, $merge$ to 11, and $next$ to 9. The call to 8 returns the triple
$(2, 11, 9)$ to the call for 7, which recurses on the second child of 7,
9. 9 returns the triple $(1, 11, 11)$. 7 is the first parent of 9, so
the depth is not incremented. $d_c$ is less than $d$, so $d$ is changed
to 1, $m$ to 11, and $next$ to 11, returning $(1, 11, 11)$ to the call
for 5. $d_c$ is less than $d$, so $d$ is changed to 1, $m$ to 11, and
$next$ to 11. There are no other children, so the function halts.

@@

\begin{figure}[htbp]
        \centering
        \vspace{3mm}
        \fontsize{7}{9}
        \begin{Verbatim}[frame=single]
Merge: 8cbd84f fd8aa2c
Author: Linus Torvalds <torvalds@linux-foundation.org>
Date:   Tue Aug 10 15:38:19 2010 -0700

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache...
...
        \end{Verbatim}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one-line summaries messages for the 24
                non-merge commits it merged. The ending ``\ldots'' is part of the log
                and represents that other commits were merged.}
        \label{fig:sampleMerge}
  \vspace{2mm}
\end{figure}

We used this information to evaluate the accuracy of the \mt model
extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016 form the Linux
repository. We computed the \mt of every commit until that date. Since
Linus Torvalds mostly does merging directly into the master branch, we
assumed that every merge by Linus is the root of a \mt, later detecting
merges that do not merge into the master branch and removing them from
the set of root merges. As described above, the log of a merge-commit
usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds
using the command \verb|git log --merges --author='Torvalds'| and
compared the number of commits stated in the log message with the number
of commits in the \mt. We also used the summaries
of the commits found in the merge (not necessarily all---see above) to
make sure those commits were in their corresponding \mt. For example, for
the merge in Figure~\ref{fig:sampleMerge} we would expect that the \mt
rooted at \mycode{8cbd84f} contains 24 commits, and the one-line
summaries corresponds to commits in that \mt. We also inspected those
with differences to make sure they were true errors. The results can be
summarized as follows:
